\documentclass[12pt,letterpaper]{article}
\usepackage{amsfonts}

\title{A little more about infinity}
\author{Ghassan Misherghi}

\begin{document}

\maketitle

\begin{abstract}
We show that both of Cantor's arguments that the reals and
$\mathcal{P}{(\infty)}$ have greater cardinality than the natrual numbers to
be false. We show that there is likely no infinity with greater cardinality than
the naturals. We show that there are no real numbers. We then defy Russel and
show that the set of all sets does in fact contain itself. We then muse on the
infinite and God.
\end{abstract}

Before begining, let me state that reasoning about $\infty$ is extremely subtle,
and we very well may be incorrect. We propose these theories to create dialogue
so we very well may advance logic and find the truth.

To deny argument that the powerset of infinity is greater than itself we only
need to show that $\infty = 2^{\infty}$. So let us look at $\lg\infty$. Suppose
$\lg\infty$ was finite. Then $\infty$ would also be finite, a contradiction. So
$\lg\infty$ must be infinite. This means it is just as big as all the naturals,
so we have that $\lg\infty=\infty$. We therefore have that
$\infty=2^{\lg\infty}=2^{\infty}$. This method is suprisingly general, working
with other increasing functions and their inverses.

We consider a one to one mapping of $\mathcal{P}(\mathbb{N})$ to $\mathbb{N}$.
Using the binary representation of the naturals, we can map any subset of the
naturals to a binary number such that for any element present in the subset,
denoted $i$, the $i$th digit is set to $1$, and $0$ otherwise. This mapping
shows that for any subset of the naturals there is exactly one number it is
mapped to and vice versa. Since there is no maximum natural this mapping will
hold, as every natural is finite. But the question arises, will this work for
the set of all naturals, an element of $\mathcal{P}(\mathbb{N})$. For it not to
work, we must have that $\infty\in\mathbb{N}$. Even so we know that
$\infty=2^\infty$, so it may.

We give more support to $\infty\in\mathbb{N}$. We ask, how many naturals are
there in $\mathbb{N}$. The answer is infinite and for each of them $+1$, aside
from $0$. So we have that $1\cdot\infty$ is a natural number, thus
$\infty\in\mathbb{N}$. 

Now let us consider Cantor's argument that the set of reals is a geater infinity
than the set of naturals. Recall that Cantor constructs a real number differing
than the diaganol of an ordering of reals. This supposedly shows that the number
is not in the set of infinite numbers that make up the diagonal, showing that it
is larger than $\infty$. We argue that if the diagonal is infinite then one
more number for which the diagonal is the same is an equivalent diagonal.
Moreover we have that $\frac{1}{\infty}=\frac{2}{2\infty}=\frac{2}{\infty}$.
Also, we can see that
$\frac{1}{\infty}=\frac{2-1}{\infty}=\frac{1-1}{\infty}=\frac{0}{\infty}$.  This
implies real numbers are always the same at infintismal places.

We propose that this implies there is no greater infinity. Suppose there is a
greater infinity than $\infty$, call it $\aleph_1$. See that
$\frac{1}{\infty}=0$. Then it must be the case that $\frac{1}{\aleph_1}=0$. We
now have that $\infty^{-1}=\aleph_1^{-1}$. It follows that
$(\infty^{-1})^{-1}=(\aleph_1^{-1})^{-1}$ thus we conclude that
$\infty=\aleph_1$. This is a contradiction, yielding that there is no greater
infinity. It is worth nothing that if the order of application is done wrongly,
this results in a divide by 0. This does lead credence to dividing by zero
resulting in $\infty$.

We also propose that there are no real numbers. Since the infinitismal places of
a real number are always $0$ (even for $\infty$, the natural), this means
significant digits must be at finite places only. This implies the real number
is actually a rational number. This places calculas in jeapordy. Consider that
$\frac{\infty*1}{\infty}=1$. Then we may assume that infinite digits of $1$ at
infinitismal decimal places may have a non-zero value. But this number is
smaller than $2$ at the largest infintismal place. So it is alwyas $0$.

Using set theoretic naturals, we need that $\infty$ contains $\infty-1$.  But
this is $\infty$ so we conclude that $\infty\in\infty$. No typing logic is
needed to show that the set of all sets contains itself. Perhaps this is
necessary for $\infty+\infty=\infty$. We add that $\infty>\infty$.

To be honest, these results baffle me. We believe that
$\infty\cdot\infty=\infty$ and that $\frac{\infty}{\infty}=\infty$.  This means
that $\frac{1}{\infty}\cdot\infty=\infty$. This produces the surprising result
that $0\cdot\infty=\infty$. $0$ and $\infty$ are inverses, so maybe it is true.
Since $\infty\cdot\infty=\infty$ and $\infty>\infty$, we can see why it isn't
$1$ and the bigger interpretation is favored. But since $0+0=0$ always, this
would imply that proofs by induction are incorrect at $\infty$. We propose a
solution. we multiply the embedded $\infty$ times zero. But since
$\infty-2$ is prsent it is back again, leaving a whole $\infty$. There is always
another outer $\infty$.

We have discredited Cantor's most famous arguments. As evidence, if there were
always a greater infinity the probability of being created would be $0$, unlike
the probability of $1$ we would expect otherwise if God exists. As a fun aside,
I advance that creation requires math, and the statement, "I must save", is a
mathmatical statement that is true, and therefore necessary for existence.  We
posit that God is really just mathmatical truth, and by living we are witnessing
our very own personalized theorem. It is our conjecture that God is within the
domain of Mathematics.

\begin{thebibliography}{9}
\bibitem{cantor1}
G. Cantor (1874) \emph{Über eine Eigenschaft des Inbegriffes aller reellen
algebraischen Zahlen}, Crelles Journal f. Mathematik 77 258 - 262.

\bibitem{cantor2}
G. Cantor (1879) \emph{Über unendliche lineare Punktmannigfaltigkeiten} Nr. 1,
Math.  Ann. 15 1-7.

\bibitem{cantor3}
G. Cantor (1890 - 1891) \emph{Über eine elementare Frage der
Mannigfaltigkeitslehre} Jahresbericht der Deutschen Math. Vereinigung I 75 -
78.

\bibitem{cantor4}
G. Cantor (1882) \emph{Über unendliche lineare Punktmannigfaltigkeiten} Nr. 3,
Math. Ann. 20 113-121. 

\end{thebibliography}

\end{document}
